### 2018-07-17 paper/design.tex
Changes disposition of design
Adds comments to design section

\section{Design of the \name file exchange system}
\label{design}
\sonja{will frame and structure A) squad overlay (prediction) B)
  global overlay (RPS) C) sphinxes (incl. sphinx, onion routing in
  general) D) SPOR and SPORES E) encryption (hybrid, payload, header)
  if not included earlier F) out-of-band}
\sonja{remove/update references to building blocks, POR}

@@

\include*{squad-overlay-design}
\include*{global-overlay-design}
\include*{sphinxes}
\include*{message-passing-design}
%\include*{file-exchange-design}

>>>>

\section{Design of the \name file exchange system}
\label{design}
\sonja{will frame and structure A) squad overlay (prediction) B)
  global overlay (RPS) C) sphinxes (incl. sphinx, onion routing in
  general) D) SPOR and SPORES E) encryption (hybrid, payload, header)
  if not included earlier F) out-of-band}
\commentDaniel{I suggest the following structure:
  A) Sphinxes
  B) SPOR (global overlay)
  C) SPORES (local overlay).
  My original idea was to make Sphinxes its own section before the design 
  section instead of a subsection in the design section.}
\sonja{remove/update references to building blocks, POR}
\commentDaniel{I removed the building blocks subsection entirely.}

@@

\include*{sphinxes}
\include*{global-overlay-design}
\include*{squad-overlay-design}
%\include*{file-exchange-design}
